Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-15 tex/results.tex
Fix typo
fix typo on dielectric name

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
For example, Wiley et al.\ show simulatinon results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.

@@

\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications from the authors of Ellis et al.\cite{ellis2016}.

>>>>

\paragraph{Method:} The main difference between the original simulations and ours is that they solve a 2D problem with the 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation. 
We lack any information about their code implementations, discretization schemes, or solver.  
We computed extinction cross-section (scattering plus absorption) while Rockstuhl et al.\ present only scattering cross-section. 
Absorption dominates in intensity over scattering in the quasistatic regime, so these results are not directly comparable. 
Nevertheless, the quantity of interest is the wavelength at which the peaks occur, and the main peaks for scattering and absorption do occur at nearly the same frequency, in this regime. 
For example, Wiley et al.\ show simulation results for a silver nanocube where the main peaks in the spectra are aligned \cite{wiley-etal-2006}.

@@

\paragraph{Dielectric data:} The study uses 6H-SiC as material, and the authors obtained their data from a source that we
were not able to replicate. Instead we are using experimental data for 4H-SiC that was provided to us 
via private communications from the authors of Ellis et al.\cite{ellis2016}.
